Stochastic Variance-Reduced Policy Gradient

### 2018-06-26 poster/poster.tex
fixed central box; removed contributions

@@

%% Policy Gradient
\newcommand{\vtheta}{\boldsymbol{\theta}}
\newcommand{\gradJ}[1]{\nabla_{#1}J_\mu(\vtheta)}
\newcommand{\vphi}{\boldsymbol{\phi}}
\newcommand{\DeltaJ}{J(\vtheta') - J(\vtheta)}
\newcommand{\gradApp}[1]{\widehat{\nabla}_{#1}J(\vtheta)}
\newcommand{\gradSim}[1]{\tilde{\nabla}_{#1}J(\vtheta)}
\newcommand{\gradRF}[1]{\hat{\nabla}_{#1}J^{RF}(\vtheta)}
\newcommand{\gradPGT}[1]{\hat{\nabla}_{#1}J^{PGT}(\vtheta)}
\newcommand{\gradGPOMDP}[1]{\hat{\nabla}_{#1}J^{G(PO)MDP}(\vtheta)}
\newcommand{\gradDown}[1]{\underline{\hat{\nabla}_{#1}J}(\vtheta)}
\newcommand{\gradUp}[1]{\overline{\hat{\nabla}_{#1}J}(\vtheta)}

%Specific
\newcommand{\Ets}[2][t]{\mathbb{E}_{#1\vert s}\left[#2\right]}
\newcommand{\Es}[1]{\mathbb{E}_{s}\left[#1\right]}
\newcommand{\Covts}[3][t]{{\mathbb{C}\text{ov}}_{#1\vert s}\left(#2,#3\right)}
\newcommand{\Covs}[2]{{\mathbb{C}\text{ov}}_{s}\left(#1,#2\right)}
\newcommand{\Varts}[2][t]{{\mathbb{V}\text{ar}}_{#1\vert s}\left[#2\right]}
\newcommand{\Vars}[1]{{\mathbb{V}\text{ar}}_{s}\left[#1\right]}
\newcommand{\gradBlack}[1]{\blacktriangledown J(#1)}
\newcommand{\gradIdeal}[1]{\dnabla J(#1)}
\newcommand{\VARRF}{V}
\newcommand{\GRADLOG}{G}
\newcommand{\VARIS}{W}
\newcommand{\HESSLOG}{F}
% short forms 
\newcommand{\wt}[1]{\widetilde{#1}}
\newcommand{\wh}[1]{\widehat{#1}}
\newcommand{\wo}[1]{\overline{#1}}
\newcommand{\wb}[1]{\overline{#1}}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Contributions}{name=contrib,column=1,row=0, span=2}{
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\begin{itemize}
		\item We design \enhance{SVRPG}, a variant of SVRG for the PG framework that explicitly addresses the \chall{challenges} of RL.
		\item We study the \textbf{convergence} properties of SVRPG
		\item  We devise \textbf{heuristics} for meta-parameter selection in order to develop a practical algorithm.
		\item We evaluate SVRPG on simulated \textbf{continuous control tasks}. 
	\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{SVRPG}{name=svrpg,column=1,span=2,row=1,below=contrib}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\item Take any \textbf{unbiased} policy gradient estimator $g(\tau|\vtheta)$ (\eg REINFORCE)
	\item \textbf{SVRG} idea: combine frequent, inaccurate \textbf{SG} estimations with rare, accurate \textbf{FG} computations.
	\item Manage \chall{non-concavity} with \textbf{smooth} policies (\eg Gaussian)
	\item Approximate \chall{infinite dataset} with a large \textbf{batch size} $N$
	\item Correct \chall{nonstationarity} with \textbf{importance weighting}
	\item At each \textbf{iteration}, update policy parameter as $\vtheta\gets\vtheta+\alpha\gradBlack{\vtheta}$ with the following \enhance{SVRPG estimator}:	
\end{itemize}
%
\vspace{1cm}
%
\begin{center}
	\tikz[overlay]{
		\node[draw=myblue, inner sep=20pt, ultra thick] {
			\Large{$
			\blacktriangledown J(\vtheta) = \wh{\nabla}_N J(\wt{\vtheta}) + \wh{\nabla}_B J({\vtheta}) - \omega(\vtheta, \wt{\vtheta}) \wh{\nabla}_B J({\wt{\vtheta}})
			$}
		};
	}
\end{center} 
%
\vspace{1.5cm}
\fbox{
\begin{minipage}[t]{.3\textwidth}
\begin{center}
	\textbf{FG term}

	\begin{equation*}
	\frac{1}{N}\sum_{i=1}^{N} g(\tau_i|\wt{\vtheta})
	\end{equation*}\\

	\begin{itemize}
		\item Trajectories sampled with \textbf{snapshot} policy $\pi_{\wt{\vtheta}}$
		\item Accurate FG approximation with $N$ samples \\$\longrightarrow$ \bad{expensive!}
		\item Updated once every $m$ iterations (one \textbf{epoch})
		to save sample efficiency
	\end{itemize}
\end{center}
\end{minipage}
}
%
\hfill\fbox{
\begin{minipage}[t]{.3\textwidth}
	\begin{center}
		\textbf{SG term}

		\begin{equation*}
		\frac{1}{B}\sum_{i=1}^{B} g(\tau_i|\vtheta)
		\end{equation*}

		\begin{itemize}
			\item Trajectories sampled with current policy $\pi_{\vtheta}$ (\textbf{online})
			\item Gradient estimation with $B<<N$ samples\\
			$\longrightarrow$ \bad{high variance!}
			\item Stabilized by the low-variance FG term
		\end{itemize}
	\end{center}
\end{minipage}
}
%
\hfill\fbox{
\begin{minipage}[t]{.25\textwidth}
	\begin{center}
			\textbf{Correction term}

			\begin{equation*}
			\frac{1}{B}\sum_{i=1}^{B}\underbrace{\omega(\tau_i|\vtheta,\wt{\vtheta})}_{\frac{p(\tau_i|\wt{\vtheta})}{p(\tau_i|\vtheta)}} g(\tau_i|\vtheta)
			\end{equation*}

			\begin{itemize}
				\item Same trajectories as the SG term
				\item But evaluated in the snapshot parameter!
				\item \textbf{Importance weighting}
		\end{itemize}
	\end{center}
\end{minipage}
}
%
}

>>>>

\usepackage{multirow}

\usepackage{tabu}

@@

%% Policy Gradient
\newcommand{\vtheta}{\boldsymbol{\theta}}
\newcommand{\gradJ}[1]{\nabla J({#1})}
\newcommand{\vphi}{\boldsymbol{\phi}}
\newcommand{\DeltaJ}{J(\vtheta') - J(\vtheta)}
\newcommand{\gradApp}[1]{\widehat{\nabla}_{#1}J(\vtheta)}
\newcommand{\gradSim}[1]{\tilde{\nabla}_{#1}J(\vtheta)}
\newcommand{\gradRF}[1]{\hat{\nabla}_{#1}J^{RF}(\vtheta)}
\newcommand{\gradPGT}[1]{\hat{\nabla}_{#1}J^{PGT}(\vtheta)}
\newcommand{\gradGPOMDP}[1]{\hat{\nabla}_{#1}J^{G(PO)MDP}(\vtheta)}
\newcommand{\gradDown}[1]{\underline{\hat{\nabla}_{#1}J}(\vtheta)}
\newcommand{\gradUp}[1]{\overline{\hat{\nabla}_{#1}J}(\vtheta)}

%Specific
\newcommand{\Ets}[2][t]{\mathbb{E}_{#1\vert s}\left[#2\right]}
\newcommand{\Es}[1]{\mathbb{E}_{s}\left[#1\right]}
\newcommand{\Covts}[3][t]{{\mathbb{C}\text{ov}}_{#1\vert s}\left(#2,#3\right)}
\newcommand{\Covs}[2]{{\mathbb{C}\text{ov}}_{s}\left(#1,#2\right)}
\newcommand{\Var}[1]{{\mathbb{V}\text{ar}}\left[#1\right]}
\newcommand{\Varts}[2][t]{{\mathbb{V}\text{ar}}_{#1\vert s}\left[#2\right]}
\newcommand{\Vars}[1]{{\mathbb{V}\text{ar}}_{s}\left[#1\right]}
\newcommand{\gradBlack}[1]{\blacktriangledown J(#1)}
\newcommand{\gradIdeal}[1]{\dnabla J(#1)}
\newcommand{\VARRF}{V}
\newcommand{\GRADLOG}{G}
\newcommand{\VARIS}{W}
\newcommand{\HESSLOG}{F}
% short forms 
\newcommand{\wt}[1]{\widetilde{#1}}
\newcommand{\wh}[1]{\widehat{#1}}
\newcommand{\wo}[1]{\overline{#1}}
\newcommand{\wb}[1]{\overline{#1}}

@@

%Fake items
\newcommand{\tabitem}[1]{~~\llap{\textbullet}~~ #1 \hfill\mbox{}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\headerbox{Contributions}{name=contrib,column=1,row=0, span=2}{
%	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	\begin{itemize}
%		\item We design \enhance{SVRPG}, a variant of SVRG for the PG framework that explicitly addresses the \chall{challenges} of RL.
%		\item We study the \textbf{convergence} properties of SVRPG
%		\item  We devise \textbf{heuristics} for meta-parameter selection in order to develop a practical algorithm.
%		\item We evaluate SVRPG on simulated \textbf{continuous control tasks}. 
%	\end{itemize}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{SVRPG}{name=svrpg,column=1,span=2,
  	row=0,%1
  	%below=contrib
  }{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
We design an \textbf{SVRG}-like algorithm for the \textbf{PG} framework.

\vspace{0.2cm}

\begin{minipage}[t]{.45\textwidth}
The easy part:
\begin{itemize}
	\item Take any \textbf{unbiased} policy gradient estimator $g(\tau|\vtheta)$ (\eg REINFORCE)
	\item \textbf{SVRG} idea: combine frequent \textbf{SG} with rare \textbf{FG} into a corrected gradient estimator $\gradBlack{\vtheta}$
	\item Two time scales: $1$ \textbf{epoch} $=m$ \textbf{iterations}
\end{itemize}
\end{minipage}
\hfill%
\begin{minipage}[t]{.45\textwidth}
Solving the RL challenges:
\begin{enumerate}
	\item Manage \chall{non-concavity} with \textbf{smooth} policies (\eg Gaussian)
	\item Approximate \chall{infinite dataset} with a large \textbf{batch size} $N$
	\item Correct \chall{nonstationarity} with \textbf{importance weighting}	
\end{enumerate}
\end{minipage}

\begin{center}
	Introducing the \enhance{SVRPG} estimator:
\end{center}

\noindent\dotfill
\begin{tabu} to \textwidth{X[c]X[2c]X[c]}
	\multirow{2}{*}{
		\shortstack{
			\textbf{FG term}\\
			$\frac{1}{N}\sum_{i=1}^{N} g(\tau_i|\wt{\vtheta})$\\
			$\tau_i\sim\wt{\vtheta}$\\
			$N$ trajectories\\
			Accurate but \bad{expensive}\\
			$\downarrow$\\
			Updated once per \textbf{epoch}
		}
	}	 
	&\tikz[baseline]{ 
		\node[draw=myblue, very thick, inner sep=5pt]{\Large{$\wh{\nabla}_N J(\wt{\vtheta}) + \wh{\nabla}_B J({\vtheta}) - \omega(\vtheta, \wt{\vtheta}) \wh{\nabla}_B J({\wt{\vtheta}})$}
		};
	}  
	\vspace{0.5cm} 
	& \multirow{2}{*}{
		\shortstack{
			\textbf{Correction term}\\
			$\frac{1}{B}\sum_{i=1}^{B}\underbrace{\omega(\tau_i|\vtheta,\wt{\vtheta})}_{\textbf{imp. weight}}g(\tau_i|\wt{\vtheta})$\\
			Trajectories from SG term \\
			Ensures SVRG properties\\
			\bad{Distribution mismatch}\\
			$\downarrow$\\
			\textbf{importance weighting}\\
			$\downarrow$\\
			\bad{new source of variance}
		}
	} \\
	& \shortstack{
		\textbf{SG term}\\
		$\frac{1}{B}\sum_{i=1}^{B} g(\tau_i|\vtheta)$\\
		$\tau_i\sim\vtheta$\\
		$B<<N$ trajectories\\
		Computed at each iteration\\
		\\Cheap but \bad{high-variance}\\
		$\downarrow$\\
		Stabilized by other terms
	}
\end{tabu}

\vspace{0.5cm}

\begin{minipage}[t]{.55\textwidth}
	Fundamental \textbf{SVRG} properties:
	\begin{enumerate}
		\item Unbiasedness: $\EVV[]{\gradBlack{\vtheta}} = \gradJ{\vtheta}$
		\item Vanishing variance: $\Var{\gradBlack{\vtheta}}\to0$ as $\vtheta\to\vtheta^*$
	\end{enumerate}
\vfill
\end{minipage}
\hfill%
\begin{minipage}[t]{.4\textwidth}
\textbf{Importance weighting}

Use samples from $\vtheta$ as taken with $\wt{\vtheta}$:
\vspace{-0.2cm}
\begin{equation*}
	w(\tau|\vtheta,\wt{\vtheta}) = \frac{p(\tau|\wt\vtheta)}{p(\tau|\vtheta)}
	\quad
	\genfrac{}{}{0pt}{}{\leftarrow \textit{target distribution}}
		{\leftarrow \textit{source distribution}}
\end{equation*}
\end{minipage}
}
